---
title: "Blur"
author: "Jason Geller"
date: "1/17/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message=FALSE)
```

# Generate Stimuli

We create two lists here: A1 and A2. One list will serve as a study (old) list and the other will serve as a test (new) list for our recognition memory test. Because I am extra particular, we will counterbalance these so each world will serve as an old word and a new world across participants. We need to make sure our words all have similar characteristics. Here we are using the wonderful `LexOPS` package where we can generate two lists. Here we filter the corpus to only include words that are: nouns, 4-6 letters in length, have a known proportion of between 90%-100%, have a low neighborhood density (OLD20 score between 1-2), high concreteness, imageability, and word frequency. See Figure below to see dimensions of word stimuli between the two lists. 

We will not run this as I already generated word lists from this and is saved in the main directory for the folder. 

```{r, eval=FALSE}

library(LexOPS)

stim <- LexOPS::lexops %>%
	subset(Length >= 5 & Length <= 6) %>%
	subset(CNC.Glasgow_Norms >= 5.3 & CNC.Glasgow_Norms <= 6.8) %>%
	subset(IMAG.Glasgow_Norms >= 5.8 & IMAG.Glasgow_Norms <= 6.8) %>%
	subset(PK.Brysbaert >= 0.9 & PK.Brysbaert <= 1) %>%
	subset(PoS.ELP %in% c("noun")) %>%
	subset(ON.OLD20 >= 1 & ON.OLD20 <= 2) %>%
	subset(Zipf.SUBTLEX_US >= 2.8 & Zipf.SUBTLEX_US <= 4.6) %>%
	split_random(2) %>%
	control_for(fpmw.SUBTLEX_US, -1000:1000) %>%
	generate(84, "balanced")


stim$A1<-toupper(stim$A1)
stim$A2<-toupper(stim$A2)

```
We want to make sure that for each list each target word appears in only one of the conditions but appears in all conditions acorss each list. 

```{r}

# create levels for lists 
blur_1 <- c("C", "HB", "LB")
blur_2 <- c("HB", "LB", "C")
blur_3 <- c("LB", "C", "HB")

```

```{r}
#stim<-read_csv(here::here("generated_stimuli_US.csv"))

L1_encoding <- stim %>%
  select(A1) %>%
  mutate(blur=rep(blur_1, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A1") 

L1_long<- long_format(stim)

L1_test <- L1_long %>%
  filter(condition=="A2") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_1, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L1_encoding, .)

L1_encoding

dplyr::count(L1_test, string, blur, study)

```

```{r}

L2_encoding <- stim %>%
  select(A1) %>%
  mutate(blur=rep(blur_2, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A1")

L2_long<- long_format(stim)

L2_test <- L2_long %>%
  filter(condition=="A2") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_2, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L2_encoding, .)

L2_encoding

dplyr::count(L2_test, blur, study)



```

```{r}

L3_encoding <- stim %>%
  select(A1) %>%
  mutate(blur=rep(blur_3, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A1")

L3_long<- long_format(stim)

L3_test <- L3_long %>%
  filter(condition=="A2") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_3, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L3_encoding, .)

L3_encoding

dplyr::count(L3_test, blur, study)



```


```{r}

L4_encoding <- stim %>%
  select(A2) %>%
  mutate(blur=rep(blur_1, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A2")

L4_long<- long_format(stim)

L4_test <- L4_long %>%
  filter(condition=="A1") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_1, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L4_encoding, .)

L4_encoding

dplyr::count(L4_test, blur, study)



```


```{r}

L5_encoding <- stim %>%
  select(A2) %>%
  mutate(blur=rep(blur_2, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A2")

L5_long<- long_format(stim)

L5_test <- L5_long %>%
  filter(condition=="A1") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_2, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L5_encoding, .)

L5_encoding

dplyr::count(L5_test, blur, study)



```

```{r}

L6_encoding <- stim %>%
  select(A2) %>%
  mutate(blur=rep(blur_3, times=28), study="old", lex="y") %>%
  dplyr::rename("string" = "A2")

L6_long<- long_format(stim)

L6_test <- L6_long %>%
  filter(condition=="A1") %>%
  select(condition, string) %>%
  mutate(blur=rep(blur_3, times=28), study="new", lex="y") %>%
  select(-condition)%>%
  rbind(L6_encoding, .)

L6_encoding

dplyr::count(L6_test, blur, study)

```

# Nonwords

We need to grab some nonwords for our LDT.  I used the ELP (could not get Wuggy to work). We dont care for nonwords so we pick 84 nonwrods to use across all 6 of our lists. We do not show nonwords during the recognition phase. 

```{r}
#nonwords<-read_csv(here::here("NonWord.csv"))



nonwrds_select <- nonwords %>%
  sample_n(84, replace=FALSE, seed=96) %>%
  select(Word)



L1_nwrds <- nonwrds_select %>% 
  mutate(blur=rep(blur_1, times=28), study="old", lex="n")



L1_nwrds$Word <- toupper(L1_nwrds$Word)

L1_nwrds$string<-gsub("'", "", L1_nwrds$string)

L1_nwrds <- rename(L1_nwrds, "string" = "Word")

```

```{r}

setwd(here::here("lists"))


L1_wrd_nw_encoding <- rbind(L1_encoding, L1_nwrds)

L1_wrd_nw_encoding <- mutate(L1_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L1_wrd_nw_encoding$string, ".png", sep="_"), paste("/images/",L1_wrd_nw_encoding$string,L1_wrd_nw_encoding$blur,".png", sep="_")))

L1_wrd_nw_encoding$stim_path<-gsub("_", "", L1_wrd_nw_encoding$stim_path)

L1_test<-mutate(L1_test, stim_path = ifelse(blur=="C", paste("/images/",L1_test$string, ".png", sep="_"), paste("/images/",L1_test$string,L1_test$blur,".png", sep="_")))

L1_test$stim_path<-gsub("_", "", L1_test$stim_path)

write.csv(L1_wrd_nw_encoding, file="L1_wrd_nw.csv")
write.csv(L1_test, file="L1_wrd_test.csv")



```

```{r}

setwd(here::here("lists"))


L2_wrd_nw_encoding <- rbind(L2_encoding, L1_nwrds)

L2_wrd_nw_encoding<- mutate(L2_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L2_wrd_nw_encoding$string, ".png", sep="_"), paste("/images/",L2_wrd_nw_encoding$string,L2_wrd_nw_encoding$blur,".png", sep="_")))

L2_wrd_nw_encoding$stim_path<-gsub("_", "", L2_wrd_nw_encoding$stim_path)


L2_test <- mutate(L2_test, stim_path = ifelse(blur=="C", paste("/images/",L2_test$string, ".png", sep="_"), paste("/images/",L2_test$string,L2_test$blur,".png", sep="_")))

L2_test $stim_path<-gsub("_", "", L2_test$stim_path)

write.csv(L2_wrd_nw_encoding, file="L2_wrd_nw.csv")
write.csv(L2_test, file="L2_wrd_test.csv")



```


```{r}

setwd(here::here("lists"))

L3_wrd_nw_encoding <- rbind(L3_encoding, L1_nwrds)

L3_wrd_nw_encoding <- mutate(L3_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L3_wrd_nw_encoding$string, ".png", sep="_"), paste("/images/",L3_wrd_nw_encoding$string,L3_wrd_nw_encoding$blur,".png", sep="_")))

L3_wrd_nw_encoding$stim_path<-gsub("_", "", L3_wrd_nw_encoding$stim_path)


L3_test<- mutate(L3_test, stim_path = ifelse(blur=="C", paste("/images/",L3_test$string, ".png", sep="_"), paste("/images/",L3_test$string,L3_test$blur,".png", sep="_")))

L3_test$stim_path<-gsub("_", "", L3_test$stim_path)

write.csv(L3_wrd_nw_encoding, file="L3_wrd_nw.csv")
write.csv(L3_test, file="L3_wrd_test.csv")

```


```{r}

setwd(here::here("lists"))


L4_wrd_nw_encoding <- rbind(L4_encoding, L1_nwrds)

L4_wrd_nw_encoding <- mutate(L4_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L4_wrd_nw_encoding$string, ".png", sep="_"), paste("/images/",L4_wrd_nw_encoding$string,L4_wrd_nw_encoding$blur,".png", sep="_")))

L4_wrd_nw_encoding$stim_path<-gsub("_", "", L4_wrd_nw_encoding$stim_path)


L4_test <- mutate(L4_test, stim_path = ifelse(blur=="C", paste("/images/",L4_test$string, ".png", sep="_"), paste("/images/",L4_test$string,L4_test$blur,".png", sep="_")))

L4_test$stim_path<-gsub("_", "", L4_test$stim_path)

write.csv(L4_wrd_nw_encoding, file="L4_wrd_nw.csv")
write.csv(L4_test, file="L4_wrd_test.csv")

```

```{r}

setwd(here::here("lists"))


L5_wrd_nw_encoding <- rbind(L5_encoding, L1_nwrds)


L5_wrd_nw_encoding <- mutate(L5_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L5_wrd_nw_encoding$string, ".png", sep="_"), paste("/images/",L5_wrd_nw_encoding$string,L5_wrd_nw_encoding$blur,".png", sep="_")))

L5_wrd_nw_encoding$stim_path<-gsub("_", "", L5_wrd_nw_encoding$stim_path)



L5_test <- mutate(L5_test, stim_path = ifelse(blur=="C", paste("/images/",L5_test$string, ".png", sep="_"), paste("/images/",L5_test$string,L5_test$blur,".png", sep="_")))

L5_test$stim_path<-gsub("_", "", L5_test$stim_path)


write.csv(L5_wrd_nw_encoding, file="L5_wrd_nw.csv")
write.csv(L5_test, file="L5_wrd_test.csv")

```

```{r}

setwd(here::here("lists"))


L6_wrd_nw_encoding <- rbind(L6_encoding, L1_nwrds)

L6_wrd_nw_encoding <- mutate(L6_wrd_nw_encoding, stim_path = ifelse(blur=="C", paste("/images/",L6_wrd_nw_encoding$string, ".png", sep=""), paste("/images/",L6_wrd_nw_encoding$string,L6_wrd_nw_encoding$blur,".png", sep="")))

L6_wrd_nw_encoding$stim_path<-gsub("_", "", L6_wrd_nw_encoding$stim_path)


L6_test <- mutate(L6_test, stim_path = ifelse(blur=="C", paste("/images/",L6_test$string, ".png", sep="_"), paste("/images/",L6_test$string,L6_test$blur,".png", sep="_")))

L6_test$stim_path<-gsub("_", "", L6_test$stim_path)


write.csv(L6_wrd_nw_encoding, file="L6_wrd_nw.csv")
write.csv(L6_test, file="L6_wrd_test.csv")

```

# Images 


```{r}

setwd(here::here("word_images")) # output images to this folder

for (i in 1:length(string)) { 
  png(paste(string[i],".png", sep="_"))
  par(bg="black")
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(string[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}
setwd(here::here("nonword_images")) # output images to this folder

for (i in 1:length(nw_strings)) { 
  png(paste(nw_strings[i],".png", sep="_"))
  par(bg="black")
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(nw_strings[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}



```

This document demonstrates a function that takes a list of word images and blurs them with an user-specified level of blur. 

# Word Lists

# The below function takes a list of images we saved above and then reads them into the blur_words functions. This will save each blurred word with level of blurring specified in the file name. 

```{r blur}

#first get a list of words we want to blurpattern

# set the wd to save the blurred words there

blur_words <- function(word_list, sigma=NULL, degree=NULL) { 
  
  if (degree=="HB") { 
  
  for (i in 1:length(word_list)) {
    
    im <- imager::load.image(word_list[i])
    word_blur <- isoblur(im,sigma, gaussian = TRUE)
    word_list[i] <- gsub(".png","", word_list[i])
    imager::save.image(word_blur,file=paste(word_list[i],"HB",".png", sep=""))
    
  }
  } 
    else  {
      
     for (i in 1:length(word_list)) {
    
    im <- imager::load.image(word_list[i])
    word_blur <- isoblur(im,sigma, gaussian = TRUE)
    word_list[i] <- gsub(".png","", word_list[i])
    imager::save.image(word_blur,file=paste(word_list[i],"LB",".png", sep=""))
     }
    }
    
  }
   
```


# Save new blurred words in a folder called blurred_images

```{r}

setwd(here::here("word_images"))

L1_test_HB<-dplyr::filter(L1_test, L1_test$blur=="HB")
L1_test_c<-dplyr::filter(L1_test, L1_test$blur=="C")
L1_test_LB<-dplyr::filter(L1_test, L1_test$blur=="LB")

L1_nw_HB<-dplyr::filter(L1_wrd_nw_encoding,L1_wrd_nw_encoding$blur=="HB", lex=="n")
L1_nw_c<-dplyr::filter(L1_wrd_nw_encoding, L1_wrd_nw_encoding$blur=="C", lex=="n")
L1_nw_LB<-dplyr::filter(L1_wrd_nw_encoding, L1_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L1_test_c$string
strings_HB<-paste(L1_test_HB$string,".png", sep="")
strings_LB<-paste(L1_test_LB$string, ".png", sep="")

strings_c_nw<- L1_nw_c$string
strings_HB_nw<-paste(L1_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L1_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep="_"))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}


blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}


blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```

```{r}

setwd(here::here("word_images"))

L2_test_HB<-dplyr::filter(L2_test, L2_test$blur=="HB")
L2_test_c<-dplyr::filter(L2_test, L2_test$blur=="C")
L2_test_LB<-dplyr::filter(L2_test, L2_test$blur=="LB")

L2_nw_HB<-dplyr::filter(L2_wrd_nw_encoding,L2_wrd_nw_encoding$blur=="HB", lex=="n")
L2_nw_c<-dplyr::filter(L2_wrd_nw_encoding, L2_wrd_nw_encoding$blur=="C", lex=="n")
L2_nw_LB<-dplyr::filter(L2_wrd_nw_encoding, L2_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L2_test_c$string
strings_HB<-paste(L2_test_HB$string,".png", sep="")
strings_LB<-paste(L2_test_LB$string, ".png", sep="")

strings_c_nw<- L2_nw_c$string
strings_HB_nw<-paste(L2_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L2_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}


blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}


blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```


```{r}

setwd(here::here("word_images"))

L3_test_HB<-dplyr::filter(L3_test, L3_test$blur=="HB")
L3_test_c<-dplyr::filter(L3_test, L3_test$blur=="C")
L3_test_LB<-dplyr::filter(L3_test, L3_test$blur=="LB")

L3_nw_HB<-dplyr::filter(L3_wrd_nw_encoding,L3_wrd_nw_encoding$blur=="HB", lex=="n")
L3_nw_c<-dplyr::filter(L3_wrd_nw_encoding, L3_wrd_nw_encoding$blur=="C", lex=="n")
L3_nw_LB<-dplyr::filter(L3_wrd_nw_encoding, L3_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L3_test_c$string
strings_HB<-paste(L3_test_HB$string,".png", sep="")
strings_LB<-paste(L3_test_LB$string, ".png", sep="")

strings_c_nw<- L3_nw_c$string
strings_HB_nw<-paste(L3_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L3_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```


```{r}

setwd(here::here("word_images"))

L4_test_HB<-dplyr::filter(L4_test, L4_test$blur=="HB")
L4_test_c<-dplyr::filter(L4_test, L4_test$blur=="C")
L4_test_LB<-dplyr::filter(L4_test, L4_test$blur=="LB")

L4_nw_HB<-dplyr::filter(L4_wrd_nw_encoding,L4_wrd_nw_encoding$blur=="HB", lex=="n")
L4_nw_c<-dplyr::filter(L4_wrd_nw_encoding, L4_wrd_nw_encoding$blur=="C", lex=="n")
L4_nw_LB<-dplyr::filter(L4_wrd_nw_encoding, L4_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L4_test_c$string
strings_HB<-paste(L4_test_HB$string,".png", sep="")
strings_LB<-paste(L4_test_LB$string, ".png", sep="")

strings_c_nw<- L4_nw_c$string
strings_HB_nw<-paste(L4_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L4_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```


```{r}

setwd(here::here("word_images"))

L6_test_HB<-dplyr::filter(L6_test, L6_test$blur=="HB")
L6_test_c<-dplyr::filter(L6_test, L6_test$blur=="C")
L6_test_LB<-dplyr::filter(L6_test, L6_test$blur=="LB")

L6_nw_HB<-dplyr::filter(L6_wrd_nw_encoding,L6_wrd_nw_encoding$blur=="HB", lex=="n")
L6_nw_c<-dplyr::filter(L6_wrd_nw_encoding, L6_wrd_nw_encoding$blur=="C", lex=="n")
L6_nw_LB<-dplyr::filter(L6_wrd_nw_encoding, L6_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L6_test_c$string
strings_HB<-paste(L6_test_HB$string,".png", sep="")
strings_LB<-paste(L6_test_LB$string, ".png", sep="")

strings_c_nw<- L6_nw_c$string
strings_HB_nw<-paste(L6_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L6_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```




```{r}

setwd(here::here("word_images"))

L5_test_HB<-dplyr::filter(L5_test, L5_test$blur=="HB")
L5_test_c<-dplyr::filter(L5_test, L5_test$blur=="C")
L5_test_LB<-dplyr::filter(L5_test, L5_test$blur=="LB")

L5_nw_HB<-dplyr::filter(L5_wrd_nw_encoding,L5_wrd_nw_encoding$blur=="HB", lex=="n")
L5_nw_c<-dplyr::filter(L5_wrd_nw_encoding, L5_wrd_nw_encoding$blur=="C", lex=="n")
L5_nw_LB<-dplyr::filter(L5_wrd_nw_encoding, L5_wrd_nw_encoding$blur=="LB", lex=="n")

strings_c<- L5_test_c$string
strings_HB<-paste(L5_test_HB$string,".png", sep="")
strings_LB<-paste(L5_test_LB$string, ".png", sep="")

strings_c_nw<- L5_nw_c$string
strings_HB_nw<-paste(L5_nw_HB$string,".png", sep="")
strings_LB_nw<-paste(L5_nw_LB$string,".png", sep="")

for (i in 1:length(strings_c)) { 
  png(paste(strings_c[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB, sigma=10, degree="HB")
blur_words(word_list = strings_LB, sigma=5, degree="LB")

setwd(here::here("nonword_images"))

for (i in 1:length(strings_c_nw)) { 
  png(paste(strings_c_nw[i],".png", sep=""))
  par(bg = 'black')
  plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')
  par(ps=36)
  text(x = 0.5, y = 0.5, paste(strings_c_nw[i]),font=2, cex=2, col = "white")
  #par(ps=18) 
  dev.off()
}

blur_words(word_list = strings_HB_nw, sigma=10, degree="HB")
blur_words(word_list = strings_LB_nw, sigma=5, degree="LB")


```



```{r}

setwd(here::here("raw_images"))

blur_words(word_list = images, sigma=14, degree="HB")

blur_words(word_list = images, sigma=7, degree="LB")


```
# Example

```{r eval=FALSE}
im <- imager::load.image(here::here("raw_images", "army_.png"))

plot(im)

im_blur <- imager::load.image(here::here("raw_images", "army_.png_blur_4_.png"))

plot(im_blur)

```
